---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# covid19viz

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/covid19viz)](https://cran.r-project.org/package=covid19viz)
<!-- badges: end -->

The goal of `covid19viz` is to access and summarize WHO sitreps for covid-19 in simple graphics.

This package works using two data repositories:

- digitalized WHO sitreps by [Fabienne Krauer](https://twitter.com/FabiKrauer) available in [fkrauer/COVID-19](https://github.com/fkrauer/COVID-19).

- Johns Hopkins University (JHU CSSE) available in [CSSEGISandData/COVID-19](https://github.com/CSSEGISandData/COVID-19).

## Installation

<!--
You can install the released version of covid19viz from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("covid19viz")
```
-->

You can install the development version of `covid19viz` using:

``` r
if(!require("remotes")) install.packages("remotes")
remotes::install_github("avallecam/covid19viz")
```

## Quick Example

### with WHO sitreps

```{r,fig.height=7.5,fig.width=9}
library(covid19viz)

# paste las update available at
# https://github.com/fkrauer/COVID-19
update <- "2020-03-10"

# apply
who_sitrep_country_report(
  update = update,
  country = "Brazil")
```

### with JHU collection

```{r}
library(tidyverse)

jhu_sitrep <- jhu_sitrep_import(source = "confirmed")

jhu_sitrep %>%
  jhu_sitrep_cleandb() %>%
  filter(country_region=="Peru") %>%
  arrange(desc(value))
```

